---
title: "Ocean Depth Map"
date: "`r Sys.Date()`"
output: html_document
---

```{r knitr_init, echo=FALSE, cache=FALSE}
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               widgetframe_widgetsdir = 'widgets')
opts_knit$set(width=75)
```

# Load Environment and Helper Functions

```{r}
# source theme for roads
source(here::here("R/themes", "depth_theme.R"))
# source ggplot2 code
source(here::here("R/ggplot2", "depth_base.R"))
library(sf)
library(raster)
library(dplyr)
library(ggplot2)
library(showtext)

# Add custom fonts
font_add_google("Hanalei", "Hanalei")
font_add_google("Hanalei Fill", "Hanalei Fill")
# automatically use showtext to render text
showtext_auto()
```

# State of Hawaii (all Islands)

```{r}
relief_100m <- data.table::fread(here::here("data/relief/100m/", "srgrhii0100a.csv"))
relief_200m <- data.table::fread(here::here("data/relief/200m/", "srgyhii200a.csv"))
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "Coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "Ocean_Depth.shp"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_100m, subtitle = "Hawaiian Islands")
saveRDS(basemap, here::here("figures/rds", "state_ocean_depth_100m_basemap.rds"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_200m,subtitle = "Hawaiian Islands")
saveRDS(basemap, here::here("figures/rds", "state_ocean_depth_200m_basemap.rds"))
```

Save images

```{r}
# save png
basemap <- ggplot(data = ocean_geo) +
    # first: draw the relief
    geom_raster(
      data = relief,
      inherit.aes = FALSE,
      aes(
        x = x,
        y = y,
        alpha = value
      )
    ) +
    # use the "alpha hack" (as the "fill" aesthetic is already taken)
    scale_alpha(
      name = "",
      range = c(0.4, 0.01),
      guide = FALSE
    ) + # suppress legend
    geom_sf(
      mapping = aes(fill = factor(depth)),
      color = "white",
      size = 0.1,
      alpha = 0.5,
      key_glyph = draw_key_dotplot
    ) +
    # draw lakes in light blue
    geom_sf(
      data = coast_geo,
      fill = "#228b22",
      color = "transparent",
      alpha = 0.2
    ) +
    scale_fill_manual(
      values = c(
        "#96F3FA",
        "#4AE2EF",
        "#00B7D6",
        "#007DAB",
        "#005A87",
        "#003B61"
      ),
      guide = "legend"
    ) +
    labs(title = "Ocean Depth Chart",
         subtitle = "",
         fill = "Depth (meters)") +
    labs(color = "") +
    guides(fill = guide_legend(override.aes = list(size = 12))) + 
  theme_minimal() +
                theme(
                        text = element_text(family = "Hanalei", color = "#5e644f"),
                        axis.line = element_blank(),
                        axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks = element_blank(),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
                        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
                        legend.background = element_rect(fill = "#f5f5f2", color = NA),
                        panel.border = element_blank(),
                        legend.text = element_text(family = "Hanalei Fill", colour="#A77B56", size=35),
                        legend.title = element_text(family = "Hanalei Fill", colour="#A77B56", size=50),
                        legend.position="bottom",
                        plot.title = element_text(family = "Hanalei", color = "#5e644f", size = 130, hjust = 0.48, vjust = -2))

ggsave(here::here("figures/png/state_ocean_depth_200m.png"), width = 210, height = 297, units = "mm", dev = ragg::agg_png())

```

This doesn't really work below yet

```{r}
file <- here::here("figures/test_basemap.png")
ragg::agg_png(
  file,
  background = "transparent",
  res = 600,
  bitsize = 16,
  width = 210,
  height = 297,
  units = "mm"
)

ggplot(data = ocean_geo) +
    # first: draw the relief
    geom_raster(
      data = relief,
      inherit.aes = FALSE,
      aes(
        x = x,
        y = y,
        alpha = value
      )
    ) +
    # use the "alpha hack" (as the "fill" aesthetic is already taken)
    scale_alpha(
      name = "",
      range = c(0.4, 0.01),
      guide = FALSE
    ) + # suppress legend
    geom_sf(
      mapping = aes(fill = factor(depth)),
      color = "white",
      size = 0.1,
      alpha = 0.5,
      key_glyph = draw_key_dotplot
    ) +
    # draw lakes in light blue
    geom_sf(
      data = coast_geo,
      fill = "#228b22",
      color = "transparent",
      alpha = 0.2
    ) +
    scale_fill_manual(
      values = c(
        "#96F3FA",
        "#4AE2EF",
        "#00B7D6",
        "#007DAB",
        "#005A87",
        "#003B61"
      ),
      guide = "legend"
    ) +
    labs(title = "Ocean Depth Chart",
         fill = "Depth (meters)") +
    labs(color = "") +
    guides(fill = guide_legend(override.aes = list(size = 12))) +
    theme_depth_lrg()
dev.off()

```

# Island of Hawaii (Big Island)

```{r}
# load the 100m subset raster file
relief_100m <- data.table::fread(here::here("data/relief/100m/", "hawaii_100m.csv"))
relief_200m <- data.table::fread(here::here("data/relief/200m/", "hawaii_200m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "hawaii_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "hawaii_depth.shp"))
## save hawaii with no relief
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_100m, subtitle = "Hawaii")
saveRDS(basemap, here::here("figures/rds", "hawaii_ocean_depth_100m_basemap.rds"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_200m, subtitle = "Hawaii")
saveRDS(basemap, here::here("figures/rds", "hawaii_ocean_depth_200m_basemap.rds"))
```

```{r}
# save png
basemap <- ggplot(data = ocean_geo) +
    # first: draw the relief
    geom_raster(
      data = relief,
      inherit.aes = FALSE,
      aes(
        x = x,
        y = y,
        alpha = value
      )
    ) +
    # use the "alpha hack" (as the "fill" aesthetic is already taken)
    scale_alpha(
      name = "",
      range = c(0.4, 0.01),
      guide = FALSE
    ) + # suppress legend
    geom_sf(
      mapping = aes(fill = factor(depth)),
      color = "white",
      size = 0.1,
      alpha = 0.5,
      key_glyph = draw_key_dotplot
    ) +
    # draw lakes in light blue
    geom_sf(
      data = coast_geo,
      fill = "#228b22",
      color = "transparent",
      alpha = 0.2
    ) +
    scale_fill_manual(
      values = c(
        "#96F3FA",
        "#4AE2EF",
        "#00B7D6",
        "#007DAB",
        "#005A87",
        "#003B61"
      ),
      guide = "legend"
    ) +
    labs(title = "Ocean Depth Chart",
         subtitle = "",
         fill = "Depth (meters)") +
    labs(color = "") +
    guides(fill = guide_legend(override.aes = list(size = 12))) + 
  theme_minimal() +
                theme(
                        text = element_text(family = "Hanalei", color = "#5e644f"),
                        axis.line = element_blank(),
                        axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks = element_blank(),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
                        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
                        legend.background = element_rect(fill = "#f5f5f2", color = NA),
                        panel.border = element_blank(),
                        legend.text = element_text(family = "Hanalei Fill", colour="#A77B56", size=35),
                        legend.title = element_text(family = "Hanalei Fill", colour="#A77B56", size=50),
                        legend.position="bottom",
                        plot.title = element_text(family = "Hanalei", color = "#5e644f", size = 130, hjust = 0.48, vjust = -2))

ggsave(here::here("figures/png/hawaii_ocean_depth_200m.png"), width = 210, height = 297, units = "mm", dev = agg_png())
```

# Island of Kauai

```{r}
# load the subset raster file
relief_100m <- data.table::fread(here::here("data/relief/100m/", "kauai_extended_100m.csv"))
relief_200m <- data.table::fread(here::here("data/relief/200m/", "kauai_extended_200m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "kauai_extended_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "kauai_depth.shp"))
## save kauai without relief
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_100m, subtitle = "Kauai")
saveRDS(basemap, here::here("figures/rds", "kauai_ocean_depth_100m_basemap.rds"))
basemap_200m <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_200m, subtitle = "Kauai")
saveRDS(basemap, here::here("figures/rds", "kauai_ocean_depth_200m_basemap.rds"))
```

```{r}
# save png
basemap <- ggplot(data = ocean_geo) +
    # first: draw the relief
    geom_raster(
      data = relief,
      inherit.aes = FALSE,
      aes(
        x = x,
        y = y,
        alpha = value
      )
    ) +
    # use the "alpha hack" (as the "fill" aesthetic is already taken)
    scale_alpha(
      name = "",
      range = c(0.4, 0.01),
      guide = FALSE
    ) + # suppress legend
    geom_sf(
      mapping = aes(fill = factor(depth)),
      color = "white",
      size = 0.1,
      alpha = 0.5,
      key_glyph = draw_key_dotplot
    ) +
    # draw lakes in light blue
    geom_sf(
      data = coast_geo,
      fill = "#228b22",
      color = "transparent",
      alpha = 0.2
    ) +
    scale_fill_manual(
      values = c(
        "#96F3FA",
        "#4AE2EF",
        "#00B7D6",
        "#007DAB",
        "#005A87",
        "#003B61"
      ),
      guide = "legend"
    ) +
    labs(title = "Ocean Depth Chart",
         subtitle = "",
         fill = "Depth (meters)") +
    labs(color = "") +
    guides(fill = guide_legend(override.aes = list(size = 12))) + 
  theme_minimal() +
                theme(
                        text = element_text(family = "Hanalei", color = "#5e644f"),
                        axis.line = element_blank(),
                        axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks = element_blank(),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
                        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
                        legend.background = element_rect(fill = "#f5f5f2", color = NA),
                        panel.border = element_blank(),
                        legend.text = element_text(family = "Hanalei Fill", colour="#A77B56", size=35),
                        legend.title = element_text(family = "Hanalei Fill", colour="#A77B56", size=50),
                        legend.position="bottom",
                        plot.title = element_text(family = "Hanalei", color = "#5e644f", size = 130, hjust = 0.48, vjust = -2))

ggsave(here::here("figures/png/kauai_ocean_depth_200m.png"), width = 210, height = 297, units = "mm", dev = agg_png())
```

# Islands of Oahu, Molokai and Maui

```{r}
# load the subset raster file
relief_100m <- data.table::fread(here::here("data/relief/100m/", "oahu_molokai_maui_100m.csv"))
relief_200m <- data.table::fread(here::here("data/relief/200m/", "oahu_molokai_maui_200m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "oahu_molokai_maui_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "oahu_molokai_maui_depth.shp"))
## save islands without relief
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_100m, subtitle = "Oahu, Molokai and Maui")
saveRDS(basemap, here::here("figures/rds", "oahu_molokai_maui_ocean_depth_100m_basemap.rds"))
# load the 200m subset rasterfile
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief_200m, subtitle = "Oahu, Molokai and Maui")
saveRDS(basemap, here::here("figures/rds", "oahu_molokai_maui_ocean_depth_200m_basemap.rds"))
```

```{r}
# save png
basemap <- ggplot(data = ocean_geo) +
    # first: draw the relief
    geom_raster(
      data = relief,
      inherit.aes = FALSE,
      aes(
        x = x,
        y = y,
        alpha = value
      )
    ) +
    # use the "alpha hack" (as the "fill" aesthetic is already taken)
    scale_alpha(
      name = "",
      range = c(0.4, 0.01),
      guide = FALSE
    ) + # suppress legend
    geom_sf(
      mapping = aes(fill = factor(depth)),
      color = "white",
      size = 0.1,
      alpha = 0.5,
      key_glyph = draw_key_dotplot
    ) +
    # draw lakes in light blue
    geom_sf(
      data = coast_geo,
      fill = "#228b22",
      color = "transparent",
      alpha = 0.2
    ) +
    scale_fill_manual(
      values = c(
        "#96F3FA",
        "#4AE2EF",
        "#00B7D6",
        "#007DAB",
        "#005A87",
        "#003B61"
      ),
      guide = "legend"
    ) +
    labs(title = "Ocean Depth Chart",
         subtitle = "",
         fill = "Depth (meters)") +
    labs(color = "") +
    guides(fill = guide_legend(override.aes = list(size = 12))) + 
  theme_minimal() +
                theme(
                        text = element_text(family = "Hanalei", color = "#5e644f"),
                        axis.line = element_blank(),
                        axis.text.x = element_blank(),
                        axis.text.y = element_blank(),
                        axis.ticks = element_blank(),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(fill = "#f5f5f2", color = NA), 
                        panel.background = element_rect(fill = "#f5f5f2", color = NA), 
                        legend.background = element_rect(fill = "#f5f5f2", color = NA),
                        panel.border = element_blank(),
                        legend.text = element_text(family = "Hanalei Fill", colour="#A77B56", size=35),
                        legend.title = element_text(family = "Hanalei Fill", colour="#A77B56", size=50),
                        legend.position="bottom",
                        plot.title = element_text(family = "Hanalei", color = "#5e644f", size = 130, hjust = 0.48, vjust = -2))

ggsave(here::here("figures/png/oahu_molokai_maui_ocean_depth_200m.png"), width = 210, height = 297, units = "mm", dev = agg_png())
```


# Trying out Magick Shadow effects

It appears this method disables x11() and it remains unseen as to whether or not when rending this into a pdf if it will maintain the custom font brought in by `showtext`. Well this doesn't seem to save a figure, it opens it in the Viewer panel - looks great!!

Now how do you export this to pdf?

```{r}
library(magick)
img <- image_graph()
state_base
dev.off()
image_shadow(img, geometry = "100x20+30+30")

```

