---
title: "Ocean Depth Map"
date: "`r Sys.Date()`"
output: html_document
---

```{r knitr_init, echo=FALSE, cache=FALSE}
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               widgetframe_widgetsdir = 'widgets')
opts_knit$set(width=75)
```

# Load Environment and Helper Functions

```{r}
# source theme for roads
source(here::here("R/themes", "depth_theme.R"))
# source ggplot2 code
source(here::here("R/ggplot2", "ocean_depth.R"))
library(sf)
library(raster)
library(dplyr)
library(ggplot2)
library(showtext)

# Add custom fonts
font_add_google("Hanalei", "Hanalei")
font_add_google("Hanalei Fill", "Hanalei Fill")
# automatically use showtext to render text
showtext_auto()
```

# State of Hawaii (all Islands)

```{r}
# load the 100m subset raster file
relief <- data.table::fread(here::here("data/relief/100m/", "srgrhii0100a.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "Coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "Ocean_Depth.shp"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
saveRDS(basemap, here::here("figures", "state_ocean_depth_100m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-100m-basemap.rds"))

# load the 200m subset rasterfile
relief <- data.table::fread(here::here("data/relief/200m/", "srgyhii200a.csv"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
# save/load
saveRDS(basemap, here::here("figures", "state_ocean_depth_200m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-200m-basemap.rds"))
```

# Island of Hawaii (Big Island)

```{r}
# load the 100m subset raster file
relief <- data.table::fread(here::here("data/relief/100m/", "hawaii_100m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "hawaii_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "hawaii_depth.shp"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
saveRDS(basemap, here::here("figures", "hawaii_ocean_depth_100m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-100m-basemap.rds"))

# load the 200m subset rasterfile
relief <- data.table::fread(here::here("data/relief/200m/", "hawaii_200m.csv"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
# save/load
saveRDS(basemap, here::here("figures", "hawaii_ocean_depth_200m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-200m-basemap.rds"))
```

# Island of Kauai

```{r}
# load the subset raster file
relief <- data.table::fread(here::here("data/relief/100m/", "kauai_extended_100m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "kauai_extended_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "kauai_depth.shp"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
saveRDS(basemap, here::here("figures", "kauai_ocean_depth_100m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-100m-basemap.rds"))

# load the 200m subset rasterfile
relief <- data.table::fread(here::here("data/relief/200m/", "kauai_extended_200m.csv"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
# save/load
saveRDS(basemap, here::here("figures", "kauai_ocean_depth_200m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-200m-basemap.rds"))
```

# Islands of Oahu, Molokai and Maui

```{r}
# load the subset raster file
relief <- data.table::fread(here::here("data/relief/100m/", "oahu_molokai_maui_100m.csv"))
# load the shapefiles with corrected projections
coast_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "oahu_molokai_maui_coastline.shp"))
ocean_geo <- sf::read_sf(here::here("data/shapefiles/corrected_projections", "oahu_molokai_maui_depth.shp"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
saveRDS(basemap, here::here("figures", "kauai_ocean_depth_100m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-100m-basemap.rds"))

# load the 200m subset rasterfile
relief <- data.table::fread(here::here("data/relief/200m/", "oahu_molokai_maui_200m.csv"))
basemap <- make_depth_map(ocean_geo = ocean_geo, coast_geo = coast_geo, relief = relief)
# save/load
saveRDS(basemap, here::here("figures", "kauai_ocean_depth_200m_basemap.rds"))
# basemap <- readRDS(here::here("figures", "ocean-depth-200m-basemap.rds"))
```

# Trying out Magick Shadow effects

It appears this method disables x11() and it remains unseen as to whether or not when rending this into a pdf if it will maintain the custom font brought in by `showtext`. Well this doesn't seem to save a figure, it opens it in the Viewer panel - looks great!!

Now how do you export this to pdf?

```{r}
library(magick)
img <- image_graph()
state_base
dev.off()
image_shadow(img, geometry = "100x20+30+30")

```

